---
title: "Unit 4 - 6 Review Starter"
author: "Group 4"
date: "11.1.21"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
library(janitor)
```

## Exercises

# Part I - Data Types and Classes

## Exercise 1 - Create some vectors

```{r month-name-vector}
month_name <- c("January", 
                "February",
                "March",
                "April",
                "May",
                "June",
                "July",
                "August",
                "September",
                "October",
                "November",
                "December")
```


#### Member 1

```{r}
classes_in_session <- c(T,
                        T,
                        T,
                        T,
                        T,
                        F,
                        F,
                        T,
                        T,
                        T,
                        T,
                        T)
```


#### Member 2

``` {r month-percip-vector}
month_percip <- c("snow",
                  "snow",
                  "snow",
                  "rain",
                  "rain",
                  "rain",
                  "rain",
                  "rain",
                  "rain",
                  "rain",
                  "snow",
                  "snow")
```

#### Member 3

```{r temperature-fahrenheit-vector}
temperature_f <- c(30, 25, 35, 40, 50, 60, 78, 80, 70, 55, 37, 28)
```

#### Member 4

```{r zodiac-vector}

zodiac <- c("Capricorn", "Aquarius", "Pisces", "Aries", "Taurus", "Gemini", "Cancer", "Leo", "Virgo", "Libra", "Scorpio", "Sagittarius")

```


#### Member 5

```{r member-5-months-days-vector}
common_days <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
```


## Exercise 2 - Combine into a data frame

```{r merge-two-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

```{r merge-two-vectors, eval = T}
classes <- tibble::tibble(
  "month_name" = month_name,
  "classes_in_session" = classes_in_session
)
```

#### Member 2

```{r merge-my-vector-with-month}
 month_precipitation <- tibble::tibble(
  "month_name" = month_name,
  "month_percip" = month_percip
)
```

#### Member 3

```{r merge-month-temp, eval = T}
month_temp <- tibble::tibble(
  "month_name" = month_name,
  "temperature_f" = temperature_f
)
```

#### Member 4

```{r merge-month-name-and-zodiac-vectors, eval = T}
 month_zodiac <- tibble::tibble(
  "month_name" = month_name,
  "zodiac" = zodiac
)
```

#### Member 5

```{r month-days-merge}
month_days <- tibble::tibble(
  "month_name" = month_name,
  "month_days" = common_days
)
```


## Exercise 3 - Try plotting with `month_name` on the x axis, then recode factors

#### Member 1

```{r month_temp_plot}
month_temp %>%
  ggplot(aes(month_name, temperature_f)) +
  geom_point()
```

```{r month_temp_plot_releveled}
month_temp %>%
  mutate(month_name = fct_relevel(month_name, "January",
                                  "February",
                                  "March",
                                  "April",
                                  "May",
                                  "June",
                                  "July",
                                  "August",
                                  "September",
                                  "October",
                                  "November",
                                  "December")) %>%
  ggplot(aes(month_name, temperature_f)) +
  geom_point()
```


#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 4 - Join all the data frames, filter randomly, and over-write vector

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.

## Exercise 5 - Try to recombine as a data frame, instead use list

```{r try-merge-vectors, eval = F}
___ <- tibble::tibble(
  "month_name" = month_name,
  "___" = ___
)
```

#### Member 1

Add your code here.

#### Member 2

Add your code here.

#### Member 3

Add your code here.

#### Member 4

Add your code here.

#### Member 5

Add your code here.
